---
title: "Initfile"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Initfile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(corrfx)
```

# Initialize subset data frames for groups(species)(Vignette in progress)

This function was created to provide for correlation analyses for intraspecific studies. So, the primary way the function works is by creating a subset for the given set of species names (spnames) and outputs csv files for each group at the user supplied path_folder. The user can specify if the output is raw(untransformed), log transformed, or rank transformed. All transformations should be done *before* creating subsets.

#### [Function inputs and meanings:]{.underline}

-   **data**: a dataframe to be split

-   **grpCol**: A string. Column to group data by

-   **dataType**: A string. Indicates what data type label for output csv files

-   **path_folder:** A string passed to 'here' function indicate folder for file placement

-   **returnCSV**: TRUE or FALSE. Do you wish to have subsets output as csv files? Default is TRUE.

## Examples:

```{r}
#for the sake of example, we'll be using PlantGrowth dataset built into R 
#Data has two columns : weight and group
head(PlantGrowth)

#convert group from factor to character. Function doesn't like factors. 
PlantGrowth$group<-as.character(PlantGrowth$group)

#create files for each control group
initfile(data = PlantGrowth, 
         grpCol = "group", 
         dataType = "RAW", returnCSV = F,
         pathFolder = "~/")

```
