---
title: "Overview_on_usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview_on_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(corrfx)
```

# Usage overview for `corrfx` functions

Here is a quick walk-through of how to use the functions within this package.

The package includes three primary functions for constructing, summarizing and presenting correlation matrices.

| Function | Use                                                                          |
|--------------|----------------------------------------------------------|
| corr_mat | Construct correlation matrices and output r values and p values.             |
| corr_adj | Convert p values from corr_mat into stars associated with the significance.  |
| finalmat | Combine the raw, log and rank correlations into one main matrices for export |

## Example code:

As an example, we will use the `mtcars` data set built into R. Note that there are file names included in the function call but these are only for exhibit the function capabilities. The default for outputCSV is false, so, at here, is to not output these files so that the environment is not cluttered.

```{r}
##Create space
library(dplyr)#for pipes and such
library(here)#for organization sakes
#explore top of the data
head(mtcars)

##Create log and rank versions of mtcars
#log transform
mtcars_log<-log10(mtcars)

#rank transform
mtcars_rank<-mtcars%>%#create new tbl with all variables for rank transformation
  dplyr::mutate_all(.,rank) #rank transform all variables

##create correlation matrix(***Note the here::here(); it allows for precise placement of output files. See ?here((here for examples)
outputs_raw<-corr_mat(dat=mtcars, raw=T, file1 = here("cor.df.csv"),
           file2 = here("p.df.csv"))
outputs_log<-corr_mat(dat=mtcars_log, raw=T, file1 = here("cor.df.log.csv"),
           file2 = here("p.df.log.csv"))
outputs_rank<-corr_mat(dat=mtcars_rank, raw=T, file1 = here("cor.df.rank.csv"),
           file2 = here("p.df.rank.csv"))

#The corr_mat function returns both a list of the correlation matrix and p values, respectively.This is in addition to the csv outputted to where you desire. 
cor.df<-outputs_raw[1]#correlation coefficients
p.df<-outputs_raw[2]#p values 

#log 
cor.log<-outputs_log[1]#correlation coefficients
p.log<-outputs_log[2]#p values 

#rank
cor.rank<-outputs_rank[1]#correlation coefficients
p.rank<-outputs_rank[2]#p values 

##Now convert the p values into stars for the final matrix
matfile_raw<-corr_adj(corData = cor.df[[1]], pData = p.df[[1]], filename="matfile.csv")
matfile_log<-corr_adj(corData = cor.log[[1]], pData = p.log[[1]], filename="matfile.log.csv")
matfile_rank<-corr_adj(corData = cor.rank[[1]], pData = p.rank[[1]], filename="matfile.rank.csv")
   
#The output here is the correlation coefficient pasted with the p values as stars 
matfile_raw #just the raw to exhibit the output.

##The last function combines the modified data frames together. 
finalmat<-finalmat(dat1=matfile_raw, dat2=matfile_log, dat3= matfile_rank, filename=here("finalmat.csv"))

##View the combined raw, log and rank correlations, respectively. 
finalmat

```
